Discrete Quantum Theories and Computing

### 2018-04-01 dissertation.tex
revised_prop_letter_ajhs.tex Fix a typo...
dissertation.lyx Updated for fitting iuphd class b532d3f3c02cf73f4424393d40c2cfa65b0eb468
dissertation.lyx Fix the order of co-chairs...

\maketitle
%data for Acceptance Page
\committeeMember{Amr A. Sabry, PhD} \committeeMember{Dylan Paul
Thurston, PhD} \committeeMember{Gerardo Ortiz, PhD} \committeeMember{Andrew
J. Hanson, PhD} \committeeMember{Shouhong Wang, PhD} \defensedate{Defense
Date} \acceptancepage

@@

\todo{The page of Bibliography is not correct?}

@@

\chapter{Quantum Interval-Valued Probability}

@@

\addcontentsline{toc}{chapter}{Bibliography} %
\begin{comment}
 \bibliographystyle{plain}
\bibliography{prop}
\end{comment}
\printbibliography

>>>>

\maketitle
%data for Acceptance Page
\committeeMember{Amr A. Sabry, PhD} \committeeMember{Gerardo
Ortiz, PhD} \committeeMember{Dylan Paul Thurston, PhD} \committeeMember{Andrew
J. Hanson, PhD} \committeeMember{Shouhong Wang, PhD} \defensedate{Defense
Date} \acceptancepage

@@

@@

\chapter{Toward a Quantum Measurement Theory with Error: Quantum Interval-Valued
Probability}

@@

\addcontentsBibliography %
\begin{comment}
 \bibliographystyle{plain}
\bibliography{prop}
\end{comment}
\printbibliography
